---
output: rmarkdown::github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ZenDNA

<!-- badges: start -->
<!-- badges: end -->

The goal of ZenDNA is to outline the Central Dogma of Molecular Biology.

## Installation

You can install the development version of ZenDNA like so:

```{r, eval = FALSE}
install.packages("devtools")
devtools::install_github("s172084/ZenDNA")
```


## Overview

ZenDNA is a package regarding the Central Dogma of Molecular Biology.

ZenDNA provides a consistent set of verbs that help you solve the most common molecular biology challenges.

* `create_dna()` generates a random sample of DNA. 

* `create_rna()` substitutes nucleotides in DNA to create RNA. 

* `create_codon()` makes codons based on the RNA sequence. 

You can learn more about the functions in `vignette(ZenDNA)`.

If you are new to ZenDNA, the best place to start is this github repository.

(If you're trying to generate a protein sequence from a DNA sequence, see `vignette(ZenDNA)`)


## Usage

**Synthesize DNA with** `create_dna()`

The first verb is `create_dna()`. It creates a string of DNA 

```{r, eval = FALSE}
dna_seq <- create_dna(300)
```

***


**Transcribe RNA with** `create_rna()`

The second verb is `create_rna()`. It creates a string of RNA 

```{r, eval = FALSE}
rna_sequence <- create_rna(dna_seq)
```

***

**Start Initiation and Elongation of RNA with** `create_codon()`

The third verb is `create_codon()`. It creates separate strings of codons

```{r, eval = FALSE}
codon_produced <- create_codon(rna_sequence)
```



## Getting help

If you encounter a clear bug, please file an issue with a minimal reproducible example on GitHub.
For questions and other discussion, please email `s172084@dtu.dk`

Please note that this project is released with a Contributor Code of Conduct. By participating in this project you agree to abide by its terms.
